### 2011-05-05 paper/paper.tex

Here, we study three Markov chain-based methods for sampling, the \emph{ball-walking} method, the \emph{metropolis} method and the \emph{hit-and-run} method, and we see how they perform comparitively in practice. The ball-walking method is the simpler of the two. We walk around the region in the following way: from a point $x$, we choose a random point in a ball around that point. If this new point lies in the convex region, then we jump to it; otherwise, we stay at $x$. We get a Markov chain $x_0, x_1, ...$, and after sufficiently many iterations, we take the point we are at to be our random point.

>>>>

Here, we study three Markov chain-based methods for sampling, the \emph{ball-walking} method, the \emph{metropolis} method and the \emph{hit-and-run} \cite{Vempala} method, and we see how they perform comparitively in practice. The ball-walking method is the simpler of the two. We walk around the region in the following way: from a point $x$, we choose a random point in a ball around that point. If this new point lies in the convex region, then we jump to it; otherwise, we stay at $x$. We get a Markov chain $x_0, x_1, ...$, and after sufficiently many iterations, we take the point we are at to be our random point.
